Master thesis

### 2017-07-20 01-Acknowledgments.Rmd
Thesis v1
Abstract 1
Akcnowledgments

I would like to thank...

- Bruno
- Stéphane
- Laurent
- Fabian
- Isabelle
- Jérôme
- Camilla
- Aurélie
- Éric
- ...

>>>>

I would like to thank Bruno Hérault and Stéphane Traissac for their guidance and advice during the whole internship. I congratulate Bruno to have been able to communicate and be reactive besides his numerous recent travels. I am grateful to Bruno and Camille Piponiot to have introduced me to the wonderful world of Bayesian statistics. All this work would not have been possible without TROLL model and the whole team that works on it : Jérôme Chave, Isabelle Maréchaux and Fabian Fischer. I thank all of the team to have introduced me to the model and guide me in its development from the opposite side of the Atlantic. I would also like to thank Laurent Descroix and people from National Forest Office who introduced me to sylviculture from french Guiana and helped me to build a realistic forest model. I also thank Aurélie Dourdain for her help to access Paracou data, Éric Marcon for his advice on biodiversity analysis, and Pascal Padolus for his patience and help wiht Tabebuia cluster. The study would not have been possible without Pascal Petronelli and all people who have contributed to Paracou and Guyafor data collection over the years. Finally I am grateful to Maxime Réjou-Méchain, Raphaël Pélissier, and AMAP colleagues, in addition to Myriam Heuertz and BIOGECO colleagues and Aurélie Cuvélier who helped me discuss the study results and build the present master thesis. To conclude, I thank everybody that played a role more or less important in the development of my internship and that I might have forgotten.

### 2017-07-20 02-Introduction.Rmd
Akcnowledgments

Our work is based on the general hypothesis of a positive relationships between biodiversity and productivity. We assumed that when a disturbance event happen, due to a higher productivity, forest with an increased diversity will recover quicker and thus be more resilient. This theoritical expectation stand on two processes: complementarity and diversity effects [@Loreau2001]. If we take a species pools with different productivity in monoculture. Their assemblage will allow theim an overall higher productivity due to a better ressources acquisition through ressource partitionning and niche differentiation. Additionally, some species will individually have an higher productivity in the assemblage than in monoculture due to facilitation from other species present in the assemblage. Complementarity effect is the addition of the better ressource acquisition and the facilitation. Now if we look at the evolution of the species assemblage over time, more competitive species will progressively dominate through competitive selection. And if competitive species are more productive, they will increase assemblage overall productivity. This ressources preemption by more competitive species is the selection effect.

>>>>

Our work is based on the general hypothesis of a positive relationships between biodiversity and productivity. We assumed that when a disturbance event happen, due to a higher productivity, forest with an increased diversity will recover quicker and thus be more resilient. This theoritical expectation stand on two processes: complementarity and selection effects [@Loreau2001]. If we take a species pool with different productivity in monoculture. Their assemblage will allow theim an overall higher productivity due to a better ressources acquisition through ressources partitionning and niche differentiation. Additionally, some species will individually have an higher productivity in the assemblage than in monoculture due to facilitation from other species present in the assemblage. Complementarity effect is the addition of the better ressource acquisition and the facilitation. Now if we look at the evolution of the species assemblage over time, more competitive species will progressively dominate through competitive selection. And if competitive species are more productive, they will increase assemblage overall productivity. This ressources preemption by more competitive species is the selection effect. Moreover, we expect the sampling effect to improve more diverse forest. A bigger initial sampling of the regional species pool in a rich forest, will allow more redundancy and a lower risk to lose important functional traits assemblages for the ecosystem when the disturbance happen.

### 2017-07-20 docs/master-thesis.tex
Akcnowledgments

I would like to thank\ldots{}

\begin{itemize}
\tightlist
\item
  Bruno
\item
  Stéphane
\item
  Camilla
\item
  Fabian
\item
  Isabelle
\item
  Laurent
\item
  Jérôme
\item
  Aurélie
\item
  Éric
\item
  Maxime
\item
  Raphaël
\item
  AMAP colleagues
\item
  Myriam
\item
  BIOGECO colleagues
\item
  Pascal Pe
\item
  Paracou team
\item
  Pascal Pa
\item
  Aurélie C
\end{itemize}

@@

Our work is based on the general hypothesis of a positive relationships
between biodiversity and productivity. We assumed that when a
disturbance event happen, due to a higher productivity, forest with an
increased diversity will recover quicker and thus be more resilient.
This theoritical expectation stand on two processes: complementarity and
diversity effects \citep{Loreau2001}. If we take a species pools with
different productivity in monoculture. Their assemblage will allow theim
an overall higher productivity due to a better ressources acquisition
through ressource partitionning and niche differentiation. Additionally,
some species will individually have an higher productivity in the
assemblage than in monoculture due to facilitation from other species
present in the assemblage. Complementarity effect is the addition of the
better ressource acquisition and the facilitation. Now if we look at the
evolution of the species assemblage over time, more competitive species
will progressively dominate through competitive selection. And if
competitive species are more productive, they will increase assemblage
overall productivity. This ressources preemption by more competitive
species is the selection effect.

@@

We found that complementary effect was insuring forest resilience in the
beginning of forest successions. We interpreted this results as the
consequence of facilitation processes. As the only ressource simulated
by TROLL is the light, the main facilitation will be light shading of
post-pioneer species by pioneer species in disturbance gaps. We found
similar results to \citet{Morin2011} regarding complementarity and light
facilitation. But the complementarity effect is reducing through time,
to let the selection effect insure forest resilience due to an inforced
dominance of more productive species. The diminishing of complementarity
effect is due to competitive selection though time in gaps succession.
But the study scale matters as shwon by \citet{Chisholm2013}. Here we
look at processes to a 16 ha scale. We do not have topography reducing
micro-environment effects, but \citet{Chisholm2013} results suggest that
complementarity will be stronger at smaller scale and could explain its
low value after forest recovery. Finally, our findings confirm results
of \citet{Tobner2016} realized on experimental forests of 4 years in low
diverse forest of Canada. They also found that selection effect was
greater than complementarity in most of the cases. In the case of
selective logging the complementarity effect will thus be the major
effect between two cutting cycles due to the cycle length (several
decades in guyana shield). High forest diversity with important species
complementarity through increased functional diversity is thus an
advantage for forest recovery between two cutting cycles in order to
maintain both productive ecosystem and sustainable management.

>>>>

I would like to thank Bruno Hérault and Stéphane Traissac for their
guidance and advice during the whole internship. I congratulate Bruno to
have been able to communicate and be reactive besides his numerous
recent travels. I am grateful to Bruno and Camille Piponiot to have
introduced me to the wonderful world of Bayesian statistics. All this
work would not have been possible without TROLL model and the whole team
that works on it : Jérôme Chave, Isabelle Maréchaux and Fabian Fischer.
I thank all of the team to have introduced me to the model and guide me
in its development from the opposite side of the Atlantic. I would also
like to thank Laurent Descroix and people from National Forest Office
who introduced me to sylviculture from french Guiana and helped me to
build a realistic forest model. I also thank Aurélie Dourdain for her
help to access Paracou data, Éric Marcon for his advice on biodiversity
analysis, and Pascal Padolus for his patience and help wiht Tabebuia
cluster. The study would not have been possible without Pascal
Petronelli and all people who have contributed to Paracou and Guyafor
data collection over the years. Finally I am grateful to Maxime
Réjou-Méchain, Raphaël Pélissier, and AMAP colleagues, in addition to
Myriam Heuertz and BIOGECO colleagues and Aurélie Cuvélier who helped me
discuss the study results and build the present master thesis. To
conclude, I thank everybody that played a role more or less important in
the development of my internship and that I might have forgotten.

@@

Our work is based on the general hypothesis of a positive relationships
between biodiversity and productivity. We assumed that when a
disturbance event happen, due to a higher productivity, forest with an
increased diversity will recover quicker and thus be more resilient.
This theoritical expectation stand on two processes: complementarity and
selection effects \citep{Loreau2001}. If we take a species pool with
different productivity in monoculture. Their assemblage will allow theim
an overall higher productivity due to a better ressources acquisition
through ressources partitionning and niche differentiation.
Additionally, some species will individually have an higher productivity
in the assemblage than in monoculture due to facilitation from other
species present in the assemblage. Complementarity effect is the
addition of the better ressource acquisition and the facilitation. Now
if we look at the evolution of the species assemblage over time, more
competitive species will progressively dominate through competitive
selection. And if competitive species are more productive, they will
increase assemblage overall productivity. This ressources preemption by
more competitive species is the selection effect. Moreover, we expect
the sampling effect to improve more diverse forest. A bigger initial
sampling of the regional species pool in a rich forest, will allow more
redundancy and a lower risk to lose important functional traits
assemblages for the ecosystem when the disturbance happen.

@@

We found that complementary effect was insuring forest resilience in the
beginning of forest successions. We interpreted this results as the
consequence of facilitation processes. As the only ressource simulated
by TROLL is the light, the main facilitation will be light shading of
post-pioneer species by pioneer species in disturbance gaps. Our results
confirm the study of \citet{Morin2011} who also highlighted the
importance of facilitation through light shading in forest resilience.
But the complementarity effect is reducing through time, to let the
selection effect insure forest resilience due to an inforced dominance
of more productive species. The diminishing of complementarity effect is
due to competitive selection though time in gaps succession. But the
study scale matters as shwon by \citet{Chisholm2013}. Here we look at
processes to a 16 ha scale. We do not have topography reducing
micro-environment effects, but \citet{Chisholm2013} results suggest that
complementarity will be stronger at smaller scale and could explain its
low value after forest recovery. Finally, our findings confirm results
of \citet{Tobner2016} realized on experimental forests of 4 years in low
diverse forest of Canada. They also found that selection effect was
greater than complementarity in most of the cases. In the case of
selective logging the complementarity effect will thus be the major
effect between two cutting cycles due to the cycle length (several
decades in guyana shield). High forest diversity with important species
complementarity through increased functional diversity is thus an
advantage for forest recovery between two cutting cycles in order to
maintain both productive ecosystem and sustainable management.
